A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-08-10 meth.tex
slight text cleanup

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{MESSAGE_11-5regions_map.pdf}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia) [yellows], Latin
      America [magenta], the Middle East and Africa [greens], the OECD (North
      America, Western Europe, and Pacific OECD) [blues], Reforming Economies
      (Eastern Europe and Former Soviet Union) [reds].  }
  \end{center}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{MESSAGE_11-5regions_map.pdf}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the RCPs with their 11-region constituents: Asia
      (Central Asia, South Asia, Pacific Asia) [yellows], Latin America
      [magenta], the Middle East and Africa [greens], the OECD (North America,
      Western Europe, and Pacific OECD) [blues], and the Reforming Economies
      (Eastern Europe and Former Soviet Union) [reds].  }
  \end{center}
\end{figure}
